Galactic Chemical Evolution Models Favor an Extended Type Ia Supernova Delay-Time Distribution

### 2024-03-19 src/tex/ms.tex
[showyourwork] overleaf sync

For simplicity and easier comparison to the results of \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively. Both elements are produced by CCSNe. \vice adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
\begin{equation}
    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_*
    \label{eq:ccsn-enrichment}
\end{equation}
where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_*$ is the SFR. 
Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$. The primary effect of these yields is to set the low-[Fe/H] ``plateau'' in [O/Fe] which represents pure CCSN enrichment. The chosen yields for this paper produce a plateau at ${\rm [O/Fe]}=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion on the effect of the CCSN yields on chemical evolution.

Following the formalism of \citet{Weinberg2017-ChemicalEquilibrium}, the rate of Fe contribution to the ISM from SNe Ia is 
\begin{equation}
    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_*\rangle_{\rm Ia} \\
\end{equation}
where $\langle \dot M_*\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia. \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
\begin{equation}
    \langle \dot M_*\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_*(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
    \label{eq:weighted-sfr}
\end{equation}
where %$\dot M_*(t)$ is the SFR at time $t$, 
%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time. The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_*$.

The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia over the full duration of the DTD, which can be expressed as:
\begin{equation}
    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_*},
    \label{eq:dtd-integral}
\end{equation}
where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_*=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}. 
Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$. This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.

@@

In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD. $f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_*}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D.
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
\vice automatically normalizes the provided function for the DTD according to this equation.
In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.

@@

The inside-out and late-burst models
% The first two models are taken from \citetalias{Johnson2021-Migration} and 
are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_*$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_*\equiv \Sigma_g/\dot\Sigma_*$. The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities. The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_*$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode). The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified. 
% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_*$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_*$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}). In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

\paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$. This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation. \citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation. [Something about $\alpha$-bimodality from another paper]. We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
\begin{equation}
    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
    \begin{cases}
        50, & t < 2.5\,\rm{Gyr} \\
        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
        2.36, & t > 3.7\,\rm{Gyr}.
    \end{cases}
    \label{eq:earlyburst-taustar}
\end{equation}
While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
\begin{equation}
    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
    \label{eq:earlyburst-ifr}
\end{equation}
where $\tau_{\rm sfh}$ is the same as in the inside-out case.
To calculate $\dot \Sigma_*$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
\begin{equation}
    \dot \Sigma_* = 
    \begin{cases}
        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
    \end{cases}
    \label{eq:earlyburst-sfr}
\end{equation}
with $\Sigma_{g,1}=5\times 10^6\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\Sigma_{g,2}=2\times 10^7\,{\rm M}_\odot\,{\rm kpc}^{-2}$.

@@

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models. We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Multi-zone model parameters
        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-methods} & Galactocentric radius \\
        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-methods} & Width of each concentric ring \\
        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
        \Delta t        & 10 Myr    & \ref{sec:multizone-methods} & Time-step size \\
        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-methods} & Maximum simulation time \\
        n               & 8         & \ref{sec:multizone-methods} & Number of stellar populations formed per ring per time-step \\
        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-methods} & Maximum radius of star formation \\
        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
        \dot M_r    & continuous    & \ref{sec:multizone-methods} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
        \hline
        % DTD
        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
        N_{\rm Ia}/M_*  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
        \hline
        % Nucleosynthetic yields
        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
        \hline
        % Star formation histories
        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
        \hline
        % One-zone parameters
        \uptau_*                        & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
        \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
    \enddata
\end{deluxetable*}
\vspace{-24pt}

We make use of the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}. The basic setup of our models follows theirs: the model Galaxy is a disk with a radius of 20 kpc and is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc. The gas in each ring is assumed to be instantaneously mixed; while star particles are allowed to migrate radially (see Appendix \ref{app:migration}), there is no exchange of gas between rings. We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr. Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_*=0$ for $R_{\rm gal}>R_{\rm SF}$ (stars are allowed to migrate past $R_{\rm SF}$, they are just not born there). We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}. We summarize these parameters, as well as those discussed in previous sub-sections, in Table \ref{tab:multizone-parameters}.

@@

\section{Results from One-Zone Models}
\label{sec:onezone-results}

% \begin{table}
%     \centering
%     \caption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
%     \begin{tabular}{ccl}
%         \hline\hline
%         Quantity & Value & \multicolumn{1}{c}{Description} \\
%         \hline
%         % $\Delta t$        & 10 Myr    & Time-step size \\
%         % $t_{\rm max}$     & 13.2 Gyr  & Maximum simulation time \\
%         % $\eta$            & 2.15      & Outflow mass-loading factor \\
%         % $\uptau_*$        & 2.0 Gyr   & SFE timescale \\
%         $\dot M_r$        & continuous    & Recycling rate \\
%         % $t_D$             & 40 Myr    & Minimum SN Ia delay time \\
%         % $M_{g,0}$         & 0         & Initial gas mass \\
%         % $\dot M_*(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
%         \hline
%     \end{tabular}
% \end{table}

% [Intro paragraph, motivation for running one-zone models]
Before running the full multi-zone models, it is useful to observe the effects of the DTD in more idealized conditions. A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence. This limits the ability to compare to observations across the disk, but it allows the models to be run in a fraction of the time and eliminates the complicating factor of stellar migration. In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.

>>>>

For simplicity and easier comparison to the results of \citetalias{Johnson2021-Migration}, we focus our analysis on O and Fe, representing the $\alpha$ and Fe-peak elements, respectively. Both elements are produced by CCSNe. \vice adopts the instantaneous recycling approximation for CCSNe, so the equation which governs CCSN enrichment as a function of star formation for some element $x$ is simply
\begin{equation}
    \dot M_x^{\rm CC} = y_x^{\rm CC} \dot M_\star
    \label{eq:ccsn-enrichment}
\end{equation}
where $y_x^{\rm CC}$ is the CCSN yield of element $x$ per unit mass of star formation, and $\dot M_\star$ is the SFR. 
Following \citetalias{Johnson2021-Migration}, who in turn adopt their CCSN yields from \citet{ChieffiLimongi2004-CCSNYields} and \citet{LimongiChieffi2006-CCSNYields}, we adopt $y_{\rm O}^{\rm CC}=0.015$ and $y_{\rm Fe}^{\rm CC}=0.0012$. The primary effect of these yields is to set the low-[Fe/H] ``plateau'' in [O/Fe] which represents pure CCSN enrichment. The chosen yields for this paper produce a plateau at ${\rm [O/Fe]}=0.45$; see \citet{Weinberg2023-CCSNYield} for more discussion on the effect of the CCSN yields on chemical evolution.

Following the formalism of \citet{Weinberg2017-ChemicalEquilibrium}, the rate of Fe contribution to the ISM from SNe Ia is 
\begin{equation}
    \dot M_{\rm Fe}^{\rm Ia} = y_{\rm Fe}^{\rm Ia} \langle \dot M_\star\rangle_{\rm Ia} \\
\end{equation}
where $\langle \dot M_\star\rangle_{\rm Ia}$ is the time-averaged SFR weighted by the DTD and $y_{\rm Fe}^{\rm Ia}$ is the Fe yield of SNe Ia. \citet{Weinberg2017-ChemicalEquilibrium} show in their Appendix A that
\begin{equation}
    \langle \dot M_\star\rangle_{\rm Ia} \equiv \frac{\int_0^t \dot M_\star(t')R_{\rm Ia}(t-t')dt'}{\int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt'}
    \label{eq:weighted-sfr}
\end{equation}
where %$\dot M_\star(t)$ is the SFR at time $t$, 
%$R_{\rm Ia}(t) dt$ is the number of SNe Ia which explode in the time interval $(t, t+dt)$ per unit mass of stars formed at $t=0$, 
$R_{\rm Ia}$ is the DTD in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$,
$t_D$ is the minimum SN Ia delay time, and $t_{\rm max}$ is the maximum simulation time. The denominator of Equation \ref{eq:weighted-sfr} is therefore the total number of SNe Ia per M$_{\odot}$ of stars formed $N_{\rm Ia}/M_\star$.

The yield $y_{\rm Fe}^{\rm Ia}$ measures the mass of Fe produced by SNe Ia over the full duration of the DTD, which can be expressed as:
\begin{equation}
    y_{\rm Fe}^{\rm Ia} = m_{\rm Fe}^{\rm Ia} \int_{t_D}^{t_{\rm max}} R_{\rm Ia}(t')dt' = m_{\rm Fe}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star},
    \label{eq:dtd-integral}
\end{equation}
where $m_{\rm Fe}^{\rm Ia}$ is the average mass of Fe produced by a single SN Ia, and $N_{\rm Ia}/M_\star=2.2\pm1\times10^{-3}\,{\rm M}_\odot^{-1}$ is the average number of SNe Ia per mass of stars formed \citep{MaozMannucci2012-SNeIaReview}. 
Adjusting the value of $y_{\rm Fe}^{\rm Ia}$ primarily affects the end point of chemical evolution tracks in [O/Fe]--[Fe/H] space. 
Following \citetalias{Johnson2021-Migration}, we adopt $y_{\rm Fe}^{\rm Ia}=0.00214$. This yield is originally adapted from the W70 model of \citet{Iwamoto1999-SNIaYields}, but it is increased slightly so that the inside-out SFH produces stars with ${\rm [O/Fe]}\approx 0.0$ by the end of the model.
\citet{Palla2021-SNIaYield} studied the effect of different SN Ia yields on GCE models in detail.

@@

In this subsection we present functional forms $f_{\rm Ia}$ describing the shape of each DTD. $f_{\rm Ia}$ does not include the normalization, so it has units of Gyr$^{-1}$ as opposed to M$_\odot^{-1}$ Gyr$^{-1}$ and ist related to $R_{\rm Ia}$ according to
% The relationship between $f_{\rm Ia}$, which has units of ${\rm Gyr}^{-1}$, and $R_{\rm Ia}$, which has units of ${\rm M}_\odot^{-1}\,{\rm Gyr}^{-1}$, is: 
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D.
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
\vice automatically normalizes the provided function for the DTD according to this equation.
In the remainder of this subsection, we discuss each form of $f_{\rm Ia}$ individually.

@@

The inside-out and late-burst models
% The first two models are taken from \citetalias{Johnson2021-Migration} and 
are run in \vice's ``star formation mode,'' where the SFR surface density $\dot\Sigma_\star$ is prescribed along with the star formation efficiency (SFE) timescale $\uptau_\star\equiv \Sigma_g/\dot\Sigma_\star$. The remaining quantities, infall rate (IFR) surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_g$, are calculated from the specified quantities. The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$, $\uptau_\star$, and an initial mass of the ISM at the onset of star formation, which we assume to be zero for all models (including those run in SFR mode). The mode in which \vice models are run makes no difference as a unique solution can always be obtained if two of the four parametric forms are specified. 
% See Appendix B of \citetalias{Johnson2021-Migration} for details on the normalization of the SFH. 
The SFH is normalized such that the model predicts an accurate total stellar mass and surface density gradient (see Appendix B of \citetalias{Johnson2021-Migration}).
We present an overview of the four SFHs in Figure \ref{fig:sfhs}, and we discuss them individually here.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/star_formation_histories.pdf}
    \caption{The surface densities of star formation $\dot \Sigma_\star$ (first row), gas infall $\dot \Sigma_{\rm in}$ (second row), and gas mass $\Sigma_g$ (third row), and the SFE timescale $\uptau_\star$ (fourth row) as functions of simulation time for our four model SFHs: inside-out (first column; see Equation \ref{eq:insideout-sfh}), late-burst (second column; see Equation \ref{eq:lateburst-sfh}), early-burst (third column; see Equations \ref{eq:earlyburst-ifr} and \ref{eq:earlyburst-taustar}), and two-infall (fourth column; see Equation \ref{eq:twoinfall-ifr}). In each panel, we plot curves for the model zones which have inner radii at 4 kpc (yellow), 6 kpc (orange), 8 kpc (red), 10 kpc (violet), 12 kpc (indigo), and 14 kpc (blue).}
    \label{fig:sfhs}
    \script{star_formation_histories.py}
\end{figure*}

@@

\paragraph{Early-burst} An extension of the model proposed by \citet{Conroy2022-ThickDisk} to explain the non-monotonic behavior of the high-$\alpha$ sequence down to ${\rm [Fe/H]}\approx-2.5$. This model features an abrupt factor $\sim20$ rise in the SFE at early times, driving an increase in the [O/Fe] abundance at the transition between the epochs of halo and thick disk formation. \citet{Stahlholdt2022-StarFormationEpochs} find evidence for a burst $\sim10$ Gyr ago which marks the beginning of a second phase of star formation. [Something about $\alpha$-bimodality from another paper]. We adopt the following formula for the time-dependence of the SFE timescale from \citet{Conroy2022-ThickDisk}:
\begin{equation}
    \frac{\uptau_{\rm EB}}{1\,\rm{Gyr}} =
    \begin{cases}
        50, & t < 2.5\,\rm{Gyr} \\
        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
        2.36, & t > 3.7\,\rm{Gyr}.
    \end{cases}
    \label{eq:earlyburst-taustar}
\end{equation}
While \citet{Conroy2022-ThickDisk} use a constant infall rate in their one-zone model, we adopt a radially-dependent infall rate which declines exponentially with time:
\begin{equation}
    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}},
    \label{eq:earlyburst-ifr}
\end{equation}
where $\tau_{\rm sfh}$ is the same as in the inside-out case.
To calculate $\dot \Sigma_\star$ from the above quantities, we modify the fiducial star formation law adopted from \citetalias{Johnson2021-Migration}, substituting $\uptau_{\rm EB}$ for the SFE timescale of molecular gas:
\begin{equation}
    \dot \Sigma_\star = 
    \begin{cases}
        \Sigma_g \uptau_{\rm EB}^{-1}, & \Sigma_g \geq \Sigma_{g,2} \\
        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
        \Sigma_g \uptau_{\rm EB}^{-1} \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1},
    \end{cases}
    \label{eq:earlyburst-sfr}
\end{equation}
with $\Sigma_{g,1}=5\times 10^6\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\Sigma_{g,2}=2\times 10^7\,{\rm M}_\odot\,{\rm kpc}^{-2}$.

@@

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of parameters and their fiducial values for our chemical evolution models. We omit some parameters that are unchanged from \citetalias{Johnson2021-Migration}; see their Table 1 for details.\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Multi-zone model parameters
        R_{\rm gal}     & [0, 20] kpc   & \ref{sec:multizone-methods} & Galactocentric radius \\
        \delta R_{\rm gal}  & 100 pc    & \ref{sec:multizone-methods} & Width of each concentric ring \\
        \Delta R_{\rm gal}  & N/A       & \ref{app:migration} & Change in orbital radius due to stellar migration \\
        p(\Delta R_{\rm gal}|\tau,R_{\rm form}) & Equation \ref{eq:radial-migration}    & \ref{app:migration} & Probability density function of radial migration distance \\
        z                   & [-3, 3] kpc                & \ref{app:migration} & Distance from Galactic midplane at present day \\
        p(z|\tau,R_{\rm final}) & Equation \ref{eq:sech-pdf}            & \ref{app:migration} & Probability density function of Galactic midplane distance\\
        \Delta t        & 10 Myr    & \ref{sec:multizone-methods} & Time-step size \\
        t_{\rm max}     & 13.2 Gyr  & \ref{sec:multizone-methods} & Maximum simulation time \\
        n               & 8         & \ref{sec:multizone-methods} & Number of stellar populations formed per ring per time-step \\
        R_{\rm SF}      & 15.5 kpc  & \ref{sec:multizone-methods} & Maximum radius of star formation \\
        M_{g,0}   & 0         & \ref{sec:sfh}     & Initial gas mass \\
        \dot M_r    & continuous    & \ref{sec:multizone-methods} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\
        \hline
        % DTD
        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay time distribution of Type Ia supernovae \\
        t_D             & 40 Myr    & \ref{sec:dtd-models}  & Minimum SN Ia delay time \\
        N_{\rm Ia}/M_\star  & $2.2\times10^{-3}$ M$_\odot^{-1}$ & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \citep{MaozMannucci2012-SNeIaReview} \\
        \hline
        % Nucleosynthetic yields
        y_{\rm O}^{\rm CC}  & 0.015     & \ref{sec:yields}  & CCSN yield of O    \\
        y_{\rm Fe}^{\rm CC} & 0.0012    & \ref{sec:yields}  & CCSN yield of Fe   \\
        y_{\rm O}^{\rm Ia}  & 0         & \ref{sec:yields}  & SN Ia yield of O       \\
        y_{\rm Fe}^{\rm Ia} & 0.00214   & \ref{sec:yields}  & SN Ia yield of Fe \\
        \hline
        % Star formation histories
        f_{\rm IO}(t|R_{\rm gal})   & Equation \ref{eq:insideout-sfh}   & \ref{sec:sfh} & Time-dependence of the inside-out SFR \\
        f_{\rm LB}(t|R_{\rm gal})   & Equation \ref{eq:lateburst-sfh}   & \ref{sec:sfh} & Time-dependence of the late-burst SFR \\
        \tau_{\rm rise}             & 2 Gyr     & \ref{sec:sfh} & SFR rise timescale for inside-out and early-burst models \\
        \uptau_{\rm EB}(t)          & Equation \ref{eq:earlyburst-taustar}  & \ref{sec:sfh}   & Time-dependence of the early-burst SFE timescale \\
        f_{\rm EB}(t|R_{\rm gal})   & Equation \ref{eq:earlyburst-ifr}  & \ref{sec:sfh} & Time-dependence of the early-burst IFR \\
        f_{\rm TI}(t|R_{\rm gal})   & Equation \ref{eq:twoinfall-ifr}   & \ref{sec:sfh} & Time-dependence of the two-infall IFR \\
        \hline
        % One-zone parameters
        \uptau_\star                    & 2 Gyr & \ref{sec:onezone-results} & SFE timescale in one-zone models \\
        \eta(R_{\rm gal}=8\,{\rm kpc})  & 2.15  & \ref{sec:onezone-results} & Outflow mass-loading factor at the solar annulus \\
        \tau_{\rm sfh}(R_{\rm gal}=8\,{\rm kpc})    & 15.1 Gyr  & \ref{sec:sfh} & SFH timescale at the solar annulus \\
    \enddata
\end{deluxetable*}
\vspace{-24pt}

We use the multi-zone GCE model tools in \vice developed by \citetalias{Johnson2021-Migration}. The basic setup of our models follows theirs. The disk is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc. Stellar populations migrate radially under the prescription we describe in Appendix \ref{app:migration}, but each ring is otherwise described by a conventional one-zone GCE model with instantaneous mixing (see discussion in Section \ref{sec:onezone-results}). Following \citetalias{Johnson2021-Migration}, we do not implement radial gas flows \citep[e.g.,][]{LaceyFall1985-RadialGasFlows,BilitewskiSchonrich2012-RadialFlows}.

We run our models with a time-step size of $\Delta t=10$ Myr up to a maximum time of $t_{\rm max}=13.2$ Gyr. Following \citetalias{Johnson2021-Migration}, we set \vice to form $n=8$ stellar populations per ring per time-step, and we set a maximum star-formation radius of $R_{\rm SF} = 15.5$ kpc, such that $\dot\Sigma_\star=0$ for $R_{\rm gal}>R_{\rm SF}$. The model has a full radial extent of 20 kpc, allowing a purely migrated population to arise in the outer 4.5 kpc. We adopt continuous recycling, which accounts for the time-dependent return of mass from all previous generations of stars \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}. We summarize these parameters, as well as those discussed in previous sub-sections, in Table \ref{tab:multizone-parameters}.

@@

\section{One-Zone Models}
\label{sec:onezone-results}

% \begin{table}
%     \centering
%     \caption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
%     \begin{tabular}{ccl}
%         \hline\hline
%         Quantity & Value & \multicolumn{1}{c}{Description} \\
%         \hline
%         % $\Delta t$        & 10 Myr    & Time-step size \\
%         % $t_{\rm max}$     & 13.2 Gyr  & Maximum simulation time \\
%         % $\eta$            & 2.15      & Outflow mass-loading factor \\
%         % $\uptau_\star$        & 2.0 Gyr   & SFE timescale \\
%         $\dot M_r$        & continuous    & Recycling rate \\
%         % $t_D$             & 40 Myr    & Minimum SN Ia delay time \\
%         % $M_{g,0}$         & 0         & Initial gas mass \\
%         % $\dot M_\star(t)$     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
%         % $\tau_{\rm rise}$ & 2.0 Gyr     & SFR rise timescale \\
%         % $\tau_{\rm sfh}$  & 15.1 Gyr  & SFR exponential \\
%         \hline
%     \end{tabular}
% \end{table}

% [Intro paragraph, motivation for running one-zone models]
Before running the full multi-zone models, it is useful to understand the effects of the DTD in more idealized conditions. A one-zone model assumes the entire gas reservoir is instantaneously mixed, removing all spatial dependence. This limits the ability to compare to observations across the disk, but it eliminates the complicating factor of stellar migration and better isolates the effects of the nucleosynthesis prescription. In this section, we compare the results from one-zone models which examine various parameters of the DTD while keeping other parameters fixed.
